---
title: 活在终端
author: whve
date: '2022-05-05'
slug: ''
categories: []
tags: []
---

test123
 
有些人的工作一直在电脑前，在网络世界随心所欲，称其为活在终端不过分吧。

打造信息茧房。

#book
#由简入易：十年学会编程
2022-?，熟悉了GitHub，学习外语，开始看源码，直到学会编程（C++、Java、html、JavaScript etc）。自动化代码，活在终端。
2020-2022，生物信息工作，一些软件使用及数据框操作。
2017-2020，读研期间，了解了一些python&R的print(“hello world”)，靠着这些基础完成了两篇SCI的数据分析。
2013-2017，本科初涉编程，大二入门语言C语言，后自学通过计算机二级考试，大三学习了Matlab。

易：
选题，收集数据，处理数据框。

做代码的搬运工，完成SCI。

简：
看R包的简介，拓展知识面。

开始接触原理，自己写函数，用GitHub管理代码，最终将自己的函数打包成R包。

感悟：通常来说，编程由简入易。可是对于我来说，走了弯路。
在此，我将重新整理R的知识，按照由简入易的顺序。

#第一年
##tidyverse 生态
###import&output
### dataflame&tibble
### key words - package 
```{r, eval = FALSE}
library(tidyverse)
help(package="tidyverse")
help(package="dplyr")
help(package="tidyr")
help(package="tibble")
help(package="ggplot2")

#查看函数源代码：
group_by # or F2
page(group_by)

group_by<-edit(group_by) # edit

###
mean
methods(mean)
mean.default

getAnywhere(group_by)
getAnywhere(pivot_longer)
# A single object matching ‘pivot_longer’ was found
# It was found in the following places
#   package:tidyr
#   namespace:tidyr
# with value
# 
# function (data, cols, names_to = "name", names_prefix = NULL, 
#     names_sep = NULL, names_pattern = NULL, names_ptypes = NULL, 
#     names_transform = NULL, names_repair = "check_unique", values_to = "value", 
#     values_drop_na = FALSE, values_ptypes = NULL, values_transform = NULL, 
#     ...) 
# {
#     ellipsis::check_dots_used()
#     UseMethod("pivot_longer")
# }
# <bytecode: 0x7fcf928244c0>
# <environment: namespace:tidyr>
help(pivot_longer)
?pivot_longer
??pivot_longer

```
#第二年
背单词
key word。


Transform or tidy
dplyr or tidyr

## dplyr function
name story:


> [The d is for dataframes, the plyr is to evoke pliers. Pronounce however you like.](https://github.com/tidyverse/dplyr/issues/1857)

[dtplyr](https://dtplyr.tidyverse.org/)
Overview
dplyr is a grammar of data manipulation, providing a consistent set of verbs that help you solve the most common data manipulation challenges:

mutate() adds new variables that are functions of existing variables
select() picks variables based on their names.
filter() picks cases based on their values.
summarise() reduces multiple values down to a single summary.
arrange() changes the ordering of the rows.
These all combine naturally with group_by() which allows you to perform any operation “by group”. You can learn more about them in vignette("dplyr"). As well as these single-table verbs, dplyr also provides a variety of two-table verbs, which you can learn about in vignette("two-table").

If you are new to dplyr, the best place to start is the data transformation chapter in R for data science.


4.2 Rows
4.2.1 filter()
4.2.2 Common mistakes
4.2.3 arrange()
4.3 Columns
4.3.1 mutate()
4.3.2 select()
4.3.3 rename()
4.3.4 relocate()
4.4 Groups
4.4.1 group_by()
4.4.2 summarise()
4.4.3 The slice_ functions
4.4.4 Grouping by multiple variables
4.4.5 Ungrouping
4.5 Case study: aggregates and sample size


## tidyr functions fall into five main categories:

“Pivotting” which converts between long and wide forms. tidyr 1.0.0 introduces pivot_longer() and pivot_wider(), replacing the older spread() and gather() functions. See vignette("pivot") for more details.

“Rectangling”, which turns deeply nested lists (as from JSON) into tidy tibbles. See unnest_longer(), unnest_wider(), hoist(), and vignette("rectangle") for more details.

Nesting converts grouped data to a form where each group becomes a single row containing a nested data frame, and unnesting does the opposite. See nest(), unnest(), and vignette("nest") for more details.

Splitting and combining character columns. Use separate() and extract() to pull a single character column into multiple columns; use unite() to combine multiple columns into a single character column.

Make implicit missing values explicit with complete(); make explicit missing values implicit with drop_na(); replace missing values with next/previous value with fill(), or a known value with replace_na().


## ggplot   
It’s hard to succinctly describe how ggplot2 works because it embodies a deep philosophy of visualisation. However, in most cases you start with ggplot(), supply a dataset and aesthetic mapping (with aes()). You then add on layers (like geom_point() or geom_histogram()), scales (like scale_colour_brewer()), faceting specifications (like facet_wrap()) and coordinate systems (like coord_flip()).


## function all

https://dplyr.tidyverse.org/reference/


# 第n年 r package

```{r, eval = FLASE}
#install.packages("bruceR")
#list data set
data(package = .packages(TRUE))

tidyverse_packages(include_self = TRUE)
```

# gwas


# 参考文献
